Interactive dashboard to monitor the COVID-19 outbreak

### 2022-03-28 paper/paper.tex
initial commit

---
title: "Interactive dashboard to monitor the COVID-19 outbreak"
type: 
author:
  - name: Thiyanga S. Talagala
    affil: a
    email: ttalagala@sjp.ac.lk
  - name: Randi Shashikala
    affil: a
affiliation:
  - num: a
    address: |
      Department of Statistics, University of Sri Jayeardenepura
bibliography: interactcadsample.bib
appendix: appendix.tex
abstract: |
  As of September 20th, 2021, 221 countries and territories are infected by the COVID-19 worldwide pandemic. Dashboards are the most often used visualization method for visualizing COVID-19 data and informing the public. The main objective of this study is to identify different features, visualization methods & improvements that should be occurred by exploring the existing dashboards and to develop a dashbored to visualize COVID-19 outbreak in Sri Lanka. We explored 15 different dashboards. The most commonly used visualization methods in dashboard development are bar charts, line charts, and interactive maps. Dashboards that fit on a single screen are preferable than others.
keywords: |
  COVID-19, Dashboard, Visualization
header-includes: |
  \usepackage{hyperref}
  \usepackage[utf8]{inputenc}
  \def\tightlist{}
output: rticles::tf_article
---

# Introduction

@@

# Literature Review

# Methodology

# Results

# Conclusions

>>>>

% interactcadsample.tex
% v1.03 - April 2017

\documentclass[]{interact}

\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
\usepackage{subfigure}% Support for small, `sub' figures and tables
%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required

\usepackage{natbib}% Citation support using natbib.sty
\bibpunct[, ]{(}{)}{;}{a}{}{,}% Citation support using natbib.sty
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty

\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}{Remark}
\newtheorem{notation}{Notation}

% see https://stackoverflow.com/a/47122900

% Pandoc citation processing

\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\def\tightlist{}

\begin{document}

\articletype{}

\title{Interactive dashboard to monitor the COVID-19 outbreak}

\author{\name{Thiyanga S. Talagala$^{a}$, Randi Shashikala$^{a}$}
\affil{$^{a}$Department of Statistics, University of Sri Jayeardenepura}
}

\thanks{CONTACT Thiyanga S.
Talagala. Email: \href{mailto:ttalagala@sjp.ac.lk}{\nolinkurl{ttalagala@sjp.ac.lk}}, Randi
Shashikala. Email: }

\maketitle

\begin{abstract}
As of September 20th, 2021, 221 countries and territories are infected
by the COVID-19 worldwide pandemic. Dashboards are the most often used
visualization method for visualizing COVID-19 data and informing the
public. The main objective of this study is to identify different
features, visualization methods \& improvements that should be occurred
by exploring the existing dashboards and to develop a dashbored to
visualize COVID-19 outbreak in Sri Lanka. We explored 15 different
dashboards. The most commonly used visualization methods in dashboard
development are bar charts, line charts, and interactive maps.
Dashboards that fit on a single screen are preferable than others.
\end{abstract}

\begin{keywords}
COVID-19, Dashboard, Visualization
\end{keywords}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{literature-review}{%
\section{Literature Review}\label{literature-review}}

\hypertarget{methodology}{%
\section{Methodology}\label{methodology}}

\hypertarget{results}{%
\section{Results}\label{results}}

\bibliographystyle{tfcad}
\bibliography{interactcadsample.bib}

\input{"appendix.tex"}

\end{document}
